---
title: "PrepareData"
author: "Jean-Francois Chartier"
date: "8 mars 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Read QM data
```{r}
QM.data=read.csv("QM_data.csv", stringsAsFactors = F, encoding = "UTF-8")
QM.data$ID=QM.data$X.U.FEFF.ID
QM.data$X.U.FEFF.ID=NULL
#=QM.data[, c(1:8, 11, 22)]
#saveRDS(QM.data, "QM.data.rds")
```

#Read event type categories file
```{r}
subToSuperCat=read.csv("sub to super categories.csv", header = T, fill = T, strip.white = T, stringsAsFactors=F, check.names=F, encoding = "UTF-8")
#subToSuperCat$ASSESSMENTS=subToSuperCat$`﻿ASSESSMENTS`
#subToSuperCat$`﻿ASSESSMENTS`=NULL
```


##create super event type categories
(deprecated)
associate one super category to a set of sub-categories
howerver, there are potentially several super categories to a save event
```{r}
#by default, set all event categories to NA
QM.data$CATEGORY=NA

for (i in 1: length(colnames(subToSuperCat))){
  cat=colnames(subToSuperCat)[i]
  print(cat)
  
  for (j in 1:length(subToSuperCat[,i])){
    x=subToSuperCat[j,i]
    if (x!=""){
      is.in = grepl(x, QM.data$SubCATEGORIES, fixed=F, ignore.case = T)
      print(sum(is.in))
      QM.data$CATEGORY[is.in]=cat
      #is.in
    }
  }
  
  
  #QM.data$CATEGORY[is.cat]=cat
}

```


```{r}
#saveRDS(QM.data, "QM.data.rds")
```



##create event type categories and duplicates events if needed
associate all super category. duplicate events
```{r}
library(magrittr)
#by default, set all event categories to NA
#QM.data$CATEGORY=NA

lapply((1:length(colnames(subToSuperCat))), function(i){
  super.cat=colnames(subToSuperCat)[i]
  print(super.cat)
  
  
  lapply(subToSuperCat[,i], function(sub.cat) {
    
    if (sub.cat!=""){
      is.in = grepl(sub.cat, QM.data$SubCATEGORIES, fixed=F, ignore.case = T)
      #print(sum(is.in))
      x=QM.data[is.in,]
      x%>%set_colnames(colnames(subToSuperCat))
      x
      #colnames(QM.data[is.in,])=colnames(subToSuperCat)
      #QM.data$CATEGORY[is.in]=super.cat
      #is.in
    }
  }) %>%data.table::rbindlist() -> events.of.super.cat
  print(nrow(events.of.super.cat))
  events.of.super.cat$CATEGORY=rep(super.cat, nrow(events.of.super.cat))
  events.of.super.cat
})%>%data.table::rbindlist() -> all.events

```

```{r}
saveRDS(all.events, "QM.data.rds")
```


#Read QM
```{r}
QM.data = readRDS("QM.data.rds")
```


#Read grabularity categorie association file
```{r}
loc.to.granu = read.csv("granularity categories.csv", header = T, fill = T, strip.white = T, stringsAsFactors=F, check.names=F, encoding = "UTF-8")
```


##create GRANULARITY categories
```{r}
#by default, set all event categories to NA
QM.data$GRANULARITY=rep("OTHER", nrow(QM.data))

for (i in 1: length(colnames(loc.to.granu))){
  cat=colnames(loc.to.granu)[i]
  print(cat)
  
  for (j in 1:length(loc.to.granu[,i])){
    x=loc.to.granu[j,i]
    print(x)
    print(length(x))
    if (x != ""){
      is.in = grepl(x, QM.data$Location.Accuracy...the.report.is.from.in.this, fixed=F, ignore.case = T)
      print(sum(is.in))
      QM.data$GRANULARITY[is.in]=cat
      #is.in
    }
  }
  
  
  #QM.data$CATEGORY[is.cat]=cat
}
```

```{r}
saveRDS(QM.data, "QM.data.rds")
```

#Read QM
```{r}
QM.data = readRDS("QM.data.rds")
```

##add corpus
```{r}
QM.data$organization=rep("Quake Map", nrow(QM.data))
```

##select colomns
```{r}
QM.data=QM.data[, c(1:4, 6:8, 11, 22:23)]
saveRDS(QM.data, "QM.data.rds")
```


#Read MSF data
```{r}
MSF.data=readRDS("MSF.data.rds")

```


##add corpus
```{r}
MSF.data$organization=rep("Doctors Without Borders", nrow(MSF.data))
```

##select colomns
```{r}
MSF.data=MSF.data[, c(2:4, 6,12, 14, 32:34)]

```

##uniformize colomn names
```{r}
MSF.data$CATEGORY=MSF.data$CATEGORY.1
MSF.data$CATEGORY.1=NULL
#encode date
date=strptime(as.character(MSF.data$DATE), "%d-%m-%Y")
date=format(date, "%Y-%m-%d")
MSF.data$INCIDENT.DATE=date
MSF.data$DATE=NULL

#encode coord
MSF.data$INCIDENT.TITLE=rep(NA, nrow(MSF.data))
MSF.data$LATITUDE=as.numeric(as.character(MSF.data$LATITUDE))
MSF.data$LONGITUDE=as.numeric(as.character(MSF.data$LONGITUDE))

#encode category
MSF.data$CATEGORY=tolower(MSF.data$CATEGORY)
MSF.data$CATEGORY[MSF.data$CATEGORY=="medical (needs/info facilities/interventions)"]="MEDICAL"
MSF.data$CATEGORY[MSF.data$CATEGORY=="relief needs (shelter/food/water)"]="RELIEF NEEDS"
MSF.data$CATEGORY[MSF.data$CATEGORY=="distribution (shelter/food/water)"]="DISTRIBUTION"
MSF.data$CATEGORY=toupper(MSF.data$CATEGORY)

#encode granularity
MSF.data$GRANULARITY=toupper(MSF.data$GRANULARITY)
MSF.data$GRANULARITY[MSF.data$GRANULARITY==toupper("Ward/exact loc")]="WARD/EXACT LOCATION"

```



#Bind 2 data set
```{r}
all.data=rbind(QM.data, MSF.data, stringsAsFactors=F)
```
##save
```{r}
saveRDS(all.data, "all.data.rds")
```

#Encode in utf8
```{r}
all.data=readRDS("all.data.rds", encoding="UTF-8")

library(stringi)

new.gran=stringi::stri_replace_all(all.data$GRANULARITY, "<U+FEFF>", fixed = T) 

all.data$GRANULARITY=new.gran

saveRDS(all.data, "all.data.rds")
```


